### 2015-01-14 paper_10_intro.tex
added overview to chapter 1 references for PMD and findbugs

    The goal of this work is to provide a basis of what data should 
    be collected by a software development organization, and how that data
    should be used to formulate a single number representing the 
    software development score of an organization. A framework to 
    achieve the score will be presented.  The  score
    is not to be comparative between organizations, but to 
    rather form a historical baseline for a specific organization.  Also, a software
    system to collect, calculate, and report the score will be presented.

%\subsection{OVERVIEW}

%    Throughout the history of software development, many values have been 
%    collected and used to measure the effectiveness of software development.

%    What is the goal? how will it help?  Expand on the thesis statement here
%    score the overall organization
%    produce a single a number score
%    don't focus too heavily on the source code

>>>>

    This work 
    provides a technique for a software development organization to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 result indicators
    of a software development organization: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.

\subsection{OVERVIEW}

    Software development organizations are no different than 
    any other business or organization.  There are: tasks
    to be completed, goals to achieve (or miss), and measurements
    to be analyzed.  One difficulty with software development
    is the varied number and amount of measurements to be used. 
    It can be difficult to determine the correct activities
    to measure and the appropriate mechanism to report the measure.
    This has led organizations to either collect too little information
    or to collect too much information.  Another problem is the 
    inconsistency of the reported measures.  It is difficult to compare
    historical performance if the same measurements are not consistent
    throughout the recent history of an organization.

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The MPI framework provides a solid foundation
    for a consistent evaluation.  It should also provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization.

    The framework will produce a single number score for each of 
    the five result indicators as well as a single overall score.  
    It will be able to provide a quick evaluation of the organization.
    The scores will enable performance to be consistently measured
    and compared.

    Other attempts at evaluating a software development organization
    have been presented, but none produce a single number score for
    the entire effort of the software development organization. 
    The following are attempts to evaluate all or parts of 
    software development.

### 2015-01-14 paper_30_measure.tex
added overview to chapter 1 references for PMD and findbugs

\section{DATA-DRIVEN SOFTWARE ENGINEERING}

@@

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD and findbugs.
    \end{itemize}

@@

\subsection{RESULT INDICATORS FOR SDOs}
    This section will cover the potential result indicators for an SDO.

\subsection{PERFORMANCE INDICATORS FOR SDOs}
    This section will cover the potential performance indicators for an SDO.

@@

Balanced scorecards are great for displaying the important information about
and organization.  However, a balanced scorecard does not specify what
exactly needs to be tracked.  It is also not specific to an SDO and 
it does produce a single number.

>>>>

\section{MEASURING A SDO}

@@

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD and findbugs \cite{PMD, Findbugs}.
    \end{itemize}

@@

\subsection{RESULT INDICATORS FOR SDO}
    This section will cover the potential result indicators for an SDO.

\subsection{KEY RESULT INDICATORS FOR SDO}

\subsection{PERFORMANCE INDICATORS FOR SDO}
    This section will cover the potential performance indicators for an SDO.

\subsection{KEY PERFORMANCE INDICATORS FOR SDO}

@@

Balanced scorecards are great for displaying the important information about
and organization.  However, a balanced scorecard does not specify what
exactly needs to be tracked.  It is also not specific to an SDO and 
it does not produce a single number.
